Group 9 Paper

### 2021-12-13 paper.Rmd
Added Code for boosting CV

 We started by fitting a logistic regression model with all the variables, and from the results above we see that there are a few non-significant variables and important ones, it is worth noting that SexM variable is is statistically significant and positive, which interesting as it means that on average men are more likely to get heart disease than women given that the other variables are the same, also, ST_SlopeFlat and ST_SlopeUp are statistically significant and the  show different signs which means that people with ST_SlopeFlat have a higher Likelyhood of having heart Disease when compared to those that have ST_SlopeUp, and this is consistent with science as ST_Slope is a important factor in the diagnosis of a heart Disease.

@@

>>>>

 We started by fitting a logistic regression model with all the variables, and from the results above we see that there are a few non-significant variables and important ones, it is worth noting that SexM variable is is statistically significant and positive, which interesting as it means that on average men are more likely to get heart disease than women given that the other variables are the same, also, ST_SlopeFlat and ST_SlopeUp are statistically significant and the  show different signs which means that people with ST_SlopeFlat have a higher Likelihood of having heart Disease when compared to those that have ST_SlopeUp, and this is consistent with science as ST_Slope is a important factor in the diagnosis of a heart Disease. Overall, for a simple method that also allows for inference, it performed relatively well with an accuracy of 0.85.

@@

```{r}
train <- read.csv("train.csv")
test <- read.csv("test.csv")

train$ChestPainType <- as.factor(train$ChestPainType)
train$Sex <- as.factor(train$Sex)
train$FastingBS <- as.factor(train$FastingBS)
train$RestingECG <- as.factor(train$RestingECG)
train$ExerciseAngina <- as.factor(train$ExerciseAngina)
train$ST_Slope <- as.factor(train$ST_Slope)

test$ChestPainType <- as.factor(test$ChestPainType)
test$Sex <- as.factor(test$Sex)
test$FastingBS <- as.factor(test$FastingBS)
test$RestingECG <- as.factor(test$RestingECG)
test$ExerciseAngina <- as.factor(test$ExerciseAngina)
test$ST_Slope <- as.factor(test$ST_Slope)

oob = trainControl(method = "oob")
cv_5 = trainControl(method = "cv", number = 5)

gbm_grid =  expand.grid(interaction.depth = 1:5,
                        n.trees = (1:5) * 200,
                        shrinkage = c(0.01,0.015,0.1),
                        n.minobsinnode = 10)

gbm_tune = train(as.factor(HeartDisease) ~ ., data = train,
                      method = "gbm",
                      trControl = cv_5,
                      verbose = FALSE,
                      tuneGrid = gbm_grid)

plot(gbm_tune)
```
